Appendix to Public Gender Egalitarianism: A Dataset of Dynamic Comparative

### 2021-06-16 paper/pge_appendix.Rmd
add Appendix C on pwe indices

# Appendix C: 
```{r create_pwe_indices}
dcpo_input_raw_public <- read_csv(here::here("data", "dcpo_input_raw_public.csv"),
                                  col_types = "cdcddcd")
public_items <- read_csv(here::here("data-raw", "public_items.csv"),
                         col_types = "ccddd")

@@

dcpo_input_public_political <- DCPOtools::format_dcpo(dcpo_input_raw_public1,
                                            scale_q = "polileader4",
                                            scale_cp = 2)
save(dcpo_input_political, file = here::here("data", "dcpo_input_political.rda"))

@@

@@

```{r political}
load(here::here("data", "political_polileader4_2_4k.rda"))

@@

```{r workplace}
load(here::here("data", "workplace_job3a_2_5k.rda"))

@@

```{r education}
load(here::here("data", "education_education4_2_5k.rda"))

@@

pge_pw <- map(1:1000, function(x) {
  pge[[x]] %>% 
    left_join(theta_res_political[[x]], by = c("country", "year")) %>% 
    left_join(theta_res_workplace[[x]], by = c("country", "year")) %>% 
    left_join(theta_res_education[[x]], by = c("country", "year"))
})

>>>>

# Appendix C: 
```{r create_pwe_indices, eval=FALSE}
dcpo_input_raw_public <- read_csv(here::here("data", "dcpo_input_raw_public.csv"),
                                  col_types = "cdcddcd")
public_items <- read_csv(here::here("data-raw", "public_items.csv"),
                         col_types = "ccddd")

@@

dcpo_input_political <- DCPOtools::format_dcpo(dcpo_input_raw_public1,
                                            scale_q = "polileader4",
                                            scale_cp = 2)
save(dcpo_input_political, file = here::here("data", "dcpo_input_political.rda"))

@@

```{r dcpo_public_b, eval=FALSE}
dcpo_input_raw_public_b <- dcpo_input_raw_public1 %>% 
  filter(political==1 | workplace==1)

dcpo_input_public_b <- DCPOtools::format_dcpo(dcpo_input_raw_public_b,
                                            scale_q = "polileader4",
                                            scale_cp = 2)
save(dcpo_input_public_b, file = here::here("data", "dcpo_input_public_b.rda"))

@@

```{r political, eval=FALSE}
load(here::here("data", "political_polileader4_2_4k.rda"))

@@

```{r workplace, eval=FALSE}
load(here::here("data", "workplace_job3a_2_5k.rda"))

@@

```{r education, eval=FALSE}
load(here::here("data", "education_education4_2_5k.rda"))

@@

pge_pw <- map(1:1000, function(x) {
  pge[[x]] %>% 
    left_join(theta_res_political[[x]], by = c("country", "year")) %>% 
    left_join(theta_res_workplace[[x]], by = c("country", "year")) %>% 
    left_join(theta_res_education[[x]], by = c("country", "year"))
}) %>% 
  map(. %>% left_join(dcpo_input$data %>% 
                         filter(item == "education4 3 or higher") %>% 
                         rowwise() %>% 
                         transmute(country = country,
                                   year = year,
                                   prop = y_r/n_r,
                                   se = sqrt((prop*(1-prop))/n),
                                   edu = rnorm(1, mean = prop, sd = se)), 
                       by = c("country", "year")))
